---
name: M Khalid Nadeem
surname: Khan 
position: "Senior Economic Advisor"
# address: "School of Physics & Chemistry, École Normale Supérieure"
phone: +44 20 7215 6885
#www: mariecurie.com
email: "Khalid.Khane@beis.gov.uk"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Professional Experience

## SENIOR ECONOMIC ADVISOR

## Head of Strategic Innovation Analysis, BEIS. March 2019-ongoing.

* Leading a team of 11 analysts to deliver major departmental priorities including increasing R&D investment in the UK, implementing the Innovation Strategy and monitoring and evaluation of £10bn annual spend. 
* Developing evidence base for setting the 2.4% target for R&D investment, the UK Innovation Strategy 2021, the R&D Roadmap 2020 including sector, technology and innovation analysis, cross country analysis to inform ministerial decisions.
* Set-up R&D portfolio, with over 150 programmes with £10bn budget, monitoring and evaluation framework, ensured development and delivery of evaluation activity through external contractors and BEIS partner organisations such as UK Research and Innovation, Innovate UK.
* Overseeing the development of business cases for large business cases  the Ensuring value-for-money for R&D £10bn portfolio this includes developing high quality business cases and high-quality monitoring and evaluation of R&D investment.
* Working with policy teams and finance to develop new R&D and innovation programmes, collaborating with partner organisations to improve quality of programme monitoring and impact evaluations through better data collection and governance.
* Briefing BEIS ministers, Senior leadership team on the balance of funding, bids preparation for HM Treasury during spending reviews (multiyear budget settlements) to make data informed decision making.
* Representing the UK at OECD committee National Experts on Science and Technology Indicators, member Cross Government Trial panel to improve use of experimental design in impact evaluation.
* Developing and implementing analytical plans for Science, Research and Innovation Directorate, managing research budget, commissioning external research and ensuring high-quality impact assessment reports.
* Leading development of evaluation data visualisation and dashboards to influence decision make on R&D funds and programmes.

## Head of R&D Appraisal and Evaluation, BEIS. September 2016 – February 2019

* Built a multidisciplinary team of analysts that provided evidence support for R&D Roadmap, M&E of the R&D portfolio, supported fiscal events, and influenced ministers and senior decision makers with clear, concise and authoritative evidence.
* Built analytical capabilities in team through commissioning research, training on soft and technical skills and implemented analytical standards to improve quality of evidence across the R&D portfolio and BEIS Partner Organisations. Managed changed effectively in team through creating culture of learning and improvement.
* Worked with partner organisations (IUK, Research Councils, Met Office, NPL) to address issues surrounding poor programme data collection, gaps in implementing M&E such as Catapults programme, and developed business case to deliver Industrial Strategy priorities through the Industrial Strategy Challenge Fund.
* Developed the business case for the first challenge led R&D investment fun, the Industrial Strategy Challenge Fund. Managed contracts with third parties for research and analytical services ranging 200-300K per year.
* Improved directorate In Year Awards process to improve fairness and efficiency.
* Provided expert advice to MHCLG and OGDs on running RCTs as a member of Cross Government Trial Panel. Advised DCMS, DfT, MoD, DEFRA and other government departments on appraising R&D projects.

## ECONOMIC ADVISOR

## Lead Analyst for the Growth Vouchers Programme, BEIS. 
July 2013 – August 2016

* Designed Randomised Controlled Trial which deliver business support to over 30 thousand small businesses across England. The programme improved access to business support for first time support users through online channels and delivered on PM’s commitment to support over 20,000 small businesses.
* Designed an online business recruitment platform to reduce delivery cost and increase access to business support across England. This addressed long-standing issue of lack of robust monitoring and evaluation data.
* Designed and successfully implemented a leadership and management support intervention with eight business schools across England to test the impact of L&M support on business Growth.
* Designed and implemented programme evaluation, with £700K budget. This was the largest RCT in business support area and influenced future business support programmes such as the current Help to Grow programme. 

## Lead Analyst on International Trade and Growth, UK Trade and Investment
June 2012 – July 2013

* Led research on barriers to exporting for small businesses in the UK. The analysis improved recruitment through better targeting of small businesses and long-term policy solutions.
* Briefed senior leaders on the policy challenge in increasing the number of exporters based on experience of other countries.
* Commissioned econometric research and business surveys to understand the link between exporting and business growth, and exporting and business innovation to improve effectiveness of UKTI’s portfolio of programmes.

## Project Manager for Developing Financial Statistics, Office for National Statistics 
April 2011 – June 2012

* Led ONS response on the coverage and reporting of financial activity after the 2008 financial crisis and worked with HMT, BoE, OBR, BEIS and FCA to have a better data on tracking risks that led to 2008 financial crisis.
* Conducted a Gap Analysis of the coverage of financial assets flow and developed UK flow-of-funds account. This account identified the counter-party risks and how failure of one action in the financial system negatively affect others and could lead to systemic risk.

## Head of Economic Methods Development Team, Office for National Statistics. 
Dec 2008 – April 2011

* Developed UK’s first account to reclassify R&D expenditure from consumption to investment and include it in the GDP estimates.
* Led Innovation Index Project for the ONS. This project was the first attempt to measure intangible capital investment (eg R&D, Design, management capabilities) in the UK and estimated contribution of intangible assets to economic growth.
* Developed economic cases for over 20 business cases for ONS investments in statistical infrastructure and improvement in delivery of statistical outputs.

## INTERNATIONAL WORK EXPERIENCE

## Adjunct Senior Research Fellow, Institute of Policy Studies, Singapore. 
July – August 2007

* Reviewed the ‘Competition Policy of Singapore’ and conducted a comparative analysis of Singapore competition regime with other small countries such as New Zealand.

## Research Associate, National Institute of Public Administration, Karachi Pakistan.  Oct 2002 – July 2006

* Supervised over 50 research projects to improve efficiency in public service delivery across many government ministries in Pakistan. 
* Designed and implemented leadership and policy analysis courses for senior Pakistani Civil Servants.

## Consultant, Asian Development Bank, Balochistan Resource Management Program Office, Pakistan June – July 2006

* Reviewed the design and delivery of Wheat Subsidy mechanism in Balochistan Province. Based on assessment then designed an alternative subsidy delivery mechanism which was implemented by the ADB to delivery subsidy to targeted beneficiaries.


```{r, eval=FALSE}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
"Oxford Programme on Negotiation", "March 2021", "Said Business School", "University of Oxford",
"Future Leaders Scheme", "2018-2020", "UK Civil Service", "UK",
"Master in Public Administration", "2007-2008", "LSE", "UK",
"Master in Public Policy", "2006-2007", "National University of Singapore", "Singapore",
"Master in Applied Economics", "2001 – 2002", "Applied Economics Research Centre", "Karachi Pakistan"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```
# Education and Training

**Oxford Programme on Negotiation, March 2021, Said Business School. University of Oxford**

**Future Leaders Scheme, 2018-2020, UK Civil Service, UK.**

**Master in Applied Sciences (Economics),  CGPR 3.59/4. May, 2001 - July, 2002 Applied Economics Research Centre, University of Karachi, Pakistan**

**Relevant Courses:**  Microeconomics I II, Macroeconomics I & II, Econometrics I, Applied Econometrics and Computer Application, and Monetary Economics

**M.A., Economics  1998 - November 2000. Bahauddin Zakariya University, Multan, Pakistan**

**Relevant Courses:**  Microeconomic Theory, Macroeconomics Theory, Mathematics used in Economics, Statistics, Economic Values of Islam, Economic Development, History of Economic Thought, Comparative Economic System, and Monetary Economics-Theory and Practice.


**Master in Public Administration (Merit- 66%) Sept, 2007 - July 2008. London School of Economics and Political Science}, GPPN Scholar**

**Relevant Courses:**  Economic Development Policy, Politics of Money in the World Economy, Politics of Economic Policy, Group Working and Leadership.
Dissertation: Supervisory Institutional Structure and Banking Sector Development around the World
**Project:** Developing Indices to Compare Performance across the UK Central Government Departments

**Master in Public Policy, (CAP: 4.71/5)  July, 2006 - May 2008 National University of Singapore (NUS), Lee Kuan Yew School of Public Policy**

**Courses:** States, Markets and International Governance; Non-state Actors in International Relations; Statistical Techniques for Public Policy; Introduction to Public Policy and Analysis; Economic and Public Policy I; Public Financial Management; Political and Organisational Analysis; Economics and Public Policy II; Institutional Design and Analysis; and Public Policy Research and Evaluation.

**Dissertation:** A Comparative Analysis of Banking Supervisory Institutional Structure in Asia-Pacific
**Independent Study Module:** Banking Sector Reform: A Case Study of Pakistan

# Honors and Awards 

* Future Leadership Scheme for High Potential Civil Servants (2018-2020)
* Lee Kuan Yew School of Public Policy Scholarship, NUS, Singapore  (2007-2008)}
* Harwin Award for Student Leadership, NUS, Singapore  (2007)}
* Lee Kuan Yew School of Public Policy Scholarship, NUS, Singapore  (2006-2007)
* American Express Bank Prize, for securing highest marks in Economics  (2004)
* Applied Economics Research Centre Scholarship, University of Karachi, Pakistan  (2001-2002)


# Publications

* Breaking the Breakers – Public Policy & Governance Case Studies from Pakistan (Edited with Syed Abu Ahmad Akif), 2021. 
* Enhancing Coverage of Financial Market Activity (with Muhammad Yaqoob), 2011. in  *Economic and Labour Market Review*: 5, pp. 82-99.
* The Characteristics of Patentors, (with Peter Evans). In *Economic and Labour Market Review*, Office for National Statistics, December 2009.
* Capitalising Research and Development: Towards New System of National Accounts, (With Lars Wenzell and Peter Evans). In Economic and Labour Market Review}, Office for National Statistics, September 2009.
* The Quality of Public Sector Management and Economic Inequality, (With Syed Abu Ahmad Akif). In The Role of Public Administration in Building a Harmonious Society }, Asian Development Bank, December 2006.
* Strategic Management in Financial Institutions: Survival in the 21st Century. In Strategic Management in Financial Institutions: Survival in the 21st Century}, Publisher, Institute of Bankers, Karachi, Pakistan, 2006.
* The Role of Civil Service Training in Strengthening Democratic Institutions in Pakistan, (with Syed Abu Ahmad Akif). In The Role of Public Administration in Alleviating Poverty and Improving Governance}, Asian Development Bank, December, 2005.
Inflation and Stock Market Performance: A Case Study of Pakistan, Saving and Development}, April 2004.   

# Reports

* Catapult Programme: A Framework for Evaluating Impact 2017, UK Government Publication. 
* Office for National Statistics. 2009. "Developing Financial Statistics for Policy." Economics and Labour Market Review-Special Issue: 3. [Team publication]  
* Innovation, knowledge spending and productivity growth in the UK: Interim report for NESTA Innovation Index project (with Jonathan Haskel, Tony Clayton, Peter Goodridge, Annarosa Pesole, David Barnett, Graeme Chamberlin, Richard Jones, and Alex Turvey) 

*Review of Wheat Subsidy Mechanism of the Food Department, Government of Balochistan, and Replacement of Existing Subsidy with Pro-Poor Targeted Atta Subsidy Mechanism in Balochistan. 

# Computer Skills 

Statistical Packages: STATA, SAS,, R, Eviews.
Applications:  Microsoft Word, Microsoft Excel, Power Point, Keynote and other common spreadsheet, and presentation software.